Titulo

### 2015-02-25 RotacionOutFlows/Paper/ms.tex
intro update

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Yamada2012,
  Chonis2013,Finkelstein2013,Ostlin14} with the aim of   exploring the
extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when
the  line is redshifted into the optical regime. With the outcoming of
new and powerfull telescopes such as the James Webb Space Telescope
new LAEs are going to be discovered.

A variety of Astrophysical problems can be studied using LAEs;
clustering \citep{Behrens13} of galaxies at high redshift,
Interstellar (ISM) and intergalactic (IGM) medium  properties
\citep{DijkstraKramer} and cosmological reionization for a recent
review see \cite{review}  among others. This motivates to study in
detail the processes that model the morphology of the \lya line.

To fully understand the observed spectra of LAEs this galaxies must be
modeled. 
However the resonant nature of the lines makes this a challenging
task.  
Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}. Recent hydrodynamical simulations have studied the
outcomming spectra of LAEs in large scale simulations, while some
others have studied detailed galaxies \citep{Verhamme12}.  
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
used in order to understand the effect of the  gas kinematics in the
Line, special attention have been devoted to model the presence   of
outflows in the galaxy. here different models have attempt to (name
the models, shell cavities etc.) 
\citep{Behrens2014}. 
Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

>>>>

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Yamada2012,
  Chonis2013,Finkelstein2013,Ostlin14} with the aim of exploring the
extragalactic Universe.  Specially at $z>=2$ since it is when
the  line is redshifted into the optical regime. With the outcoming of
new and powerfull telescopes such as the James Webb Space Telescope
new LAEs are going to be discovered with a better resultation and at
higher redshifts.

This observations have a direct impact in studing the reionization epoch
see \cite{review} fore more details and references in within,
properties of the interstellar medium (ISM) and the intergalactic medium (IGM)
\citep{Behrens13} \citep{DijkstraKramer}, constraining star formation 
rates, understanding galaxy luminosity functions \cite{Max} and
studying the large scale structure of the Universe. In all of this
studies is required a understanding the processes 
that model the morphology and the emission of the \lya line.

To fully understand the observed spectra of the LAEs this galaxies must be
modeled. However the resonant nature of the lines makes this a challenging
task. Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}. Recent hydrodynamical simulations have studied the
outcomming spectra of LAEs in large scale simulations, while some
others have studied detailed galaxies \citep{Verhamme12}.  
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
used in order to understand the effect of the  gas kinematics in the
Line, special attention have been devoted to model the presence   of
outflows in the galaxy. Here different models have attempt to 
simulate more realistic situations involving shlle models, cavities and-- 
\citep{Behrens2014}. Most recently \cite{Garavito14} have studied in 
detail the effect of rotation on the lyman alpha line.
